Optimal Task Phasing for End-To-End Latency in Harmonic Systems and Semi-Harmonic Automotive Systems

### 2024-10-02 paper.tex
notes matthias
Added first versions eval plots

>>>>

	\mario{Plan for plots:

	1) Boxplot: optimal/synchronous phasing

	2) Line graph (avergage/median; Baseline: Davare):
	- Davare
	- Synchronous
	- Related Work
	- Random Offset
	- Optimal

	All: x-axis=number of tasks in chain}

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/LatencyComp.pdf}
	\caption{Comparison of latency under worst-case phasing, synchronous release and optimal phasing. Normalized to the hyperperiod of the chain.}
	\label{fig:latencyComp}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/LatencyReduction.pdf}
	\caption{Latency reduction with optimal phasing compared to synchronous release.}
	\label{fig:latencyReduction}
\end{figure}

\begin{figure}
	\includegraphics[width=\columnwidth]{plots/AnalysisTimeComp.pdf}
	\caption{Analysis time of the different approaches.}
	\label{fig:analysisTime}
\end{figure}
